### 2018-04-06 Sections/encrypted_cloud_quantum_computing.tex
Added stuff to Section XXIII

\sihui{Although homomorphic encryption protocols have been around for a few decades [cite], classical FHE} has only been described very recently \cite{bib:gentry2009fully, bib:van2010fully}. \sihui{In Gentry's seminal paper, he showed that if a homomorphic encryption scheme can evaluate its own decryption circuit, and also slightly augmented versions of it--a feature he calls {\it bootstrapping}, one can construct a FHE scheme from it. Then he constructed a homomorphic encryption protocol using ideal lattices, and via a clever transformation that decreases the complexity of its decryption circuit, showed that it is bootstrappable with respect to a universal set of gates.}

 \comment{What is the overhead in classical resources? What about classical blind computation -- impossible? Brief outline of how classical approach works.}

>>>>

\sihui{Although homomorphic encryption protocols have been around for a few decades [cite], classical FHE} has only been described very recently \cite{bib:gentry2009fully, bib:van2010fully}. \sihui{In Gentry's seminal paper, he showed that if a homomorphic encryption scheme can evaluate its own decryption circuit, and also slightly augmented versions of it--a feature he calls {\it bootstrapping}, one can construct a FHE scheme from it. Then he constructed a homomorphic encryption protocol using ideal lattices, and via a clever transformation that decreases the complexity of its decryption circuit, showed that it is bootstrappable with respect to a universal set of gates. For a security parameter $\lambda$, Gentry's scheme has a $\widetilde{O}(\lambda^6)$ \footnote{The tilde in the big O notation means that we are ignoring logarithmic factors.} bit bound on complexity for refreshing a ciphertext corresponding to a 1-bit plaintext \cite{bib:Gentrythesis}. This was subsequently reduced to $\widetilde{O}(\lambda^{3.5})$ \cite{bib:Damien2010}, $\widetilde{O}(\lambda)$ \cite{bib:Brakerski2011}, and ${\rm polylog (\lambda)}$ for any width-$\Omega(\lambda)$ circuit with $t$ gates \cite{bib:Craig2012}. }
